Provisional Title

### 2021-05-06 draft/draft.tex
added missing Rsquared values to draft

\begin{figure}[!h]
\centering
\includegraphics[width=15cm,keepaspectratio]{figs/fig2.pdf}
\caption{\textbf{Co-selection in microbial community coalescence.}
\textbf{a.}~Coalescence outcomes are quantified by the relative Bray-Curtis similarity
($Q$) between the coalesced and invasive communities (\methodsref{methods:metrics}).
These outcomes are predicted by the pairwise competition between the invasive and
resident dominant
species ($R^2=X$ for glutamine and $X$ for citrate). This is consistent with a scenario of
top-down positive co-selection where dominants recruit their cohorts for the final
coalesced community.
\textbf{b.}~We represent the frequency reached by
the invasive dominant species when they invade the resident communities on their own versus
when they are in the company of their cohort.
Three scenarios are possible: green and red
shaded areas represent limit cases of positive (recruitment) or negative (antagonism)
bottom-up co-selection, gray area corresponds to situations where invasive dominant
species can invade with equal success regardless of the presence of their cohorts.
Data shows that positive co-selection is common, whereas antagonistic
co-selection is rare in our experiments.
\textbf{c-d.} Simulations of community coalescence with a consumer-resource model
are able to capture these trends.}
\label{fig2}
\end{figure}

>>>>

\begin{figure}[!h]
\centering
\includegraphics[width=15cm,keepaspectratio]{figs/fig2.pdf}
\caption{\textbf{Co-selection in microbial community coalescence.}
\textbf{a.}~Coalescence outcomes are quantified by the relative Bray-Curtis similarity
($Q$) between the coalesced and invasive communities (\methodsref{methods:metrics}).
These outcomes are predicted by the pairwise competition between the invasive and
resident dominant
species ($R^2=0.15$ for glutamine and $R^2=0.57$ for citrate). This is consistent with a scenario of
top-down positive co-selection where dominants recruit their cohorts for the final
coalesced community.
\textbf{b.}~We represent the frequency reached by
the invasive dominant species when they invade the resident communities on their own versus
when they are in the company of their cohort.
Three scenarios are possible: green and red
shaded areas represent limit cases of positive (recruitment) or negative (antagonism)
bottom-up co-selection, gray area corresponds to situations where invasive dominant
species can invade with equal success regardless of the presence of their cohorts.
Data shows that positive co-selection is common, whereas antagonistic
co-selection is rare in our experiments.
\textbf{c-d.} Simulations of community coalescence with a consumer-resource model
are able to capture these trends.}
\label{fig2}
\end{figure}
